### 2014-10-31 fundamentals/intro.tex
removes proliferation metric phrasing

Nuclear fuel cycle simulators can drive \gls{RDD} by calculating `metrics', 
quantitative measures of performance that 
can be compared among fuel cycle options. The feasibility of technology 
strategies, dynamics of transitions between fuel cycles, and many other 
measures of performance can be expressed in terms of these metrics. For example, 
economic feasibility is often measured in \gls{LCOE} while proliferation risk 
can be proportional to total kilograms of separated Pu, and environmental 
performance might be measured in spent fuel volume, toxicity, or mined uranium.

>>>>

Nuclear fuel cycle simulators can drive \gls{RDD} by calculating `metrics', 
quantitative measures of performance that 
can be compared among fuel cycle options. The feasibility of technology 
strategies, dynamics of transitions between fuel cycles, and many other 
measures of performance can be expressed in terms of these metrics. For example, 
economic feasibility is often measured in \gls{LCOE}
while environmental performance might be measured in spent fuel volume, 
  toxicity, or mined uranium.
